Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-07-30 paper/responseRound2/AJPResponseLetter.tex

\item p5, right column, para 2: The first two sentences seem to contradict each other. Can you clarify? 
\begin{itemize}
\item The first sentence refers to our prior beleifs before we begin any analysis or look at the data. Without any prior knowledge, we believe that the signal is equally likely to have started in any frequency bin within the range considered. The second sentence is the first stage of the algorithm once we have begun the analysis and looked at the data. We have added clarification to the text to explain this. 
\end{itemize}

\item p5, right column, para 1: What does ``marginalisation'' mean? Do you mean no hard barriers?
\item This statement was added in response to referee 3, who asked about marginalization and spotted an error in this equation in the initial version of the manuscript. If we have a probability distribution in multiple dimensions, but we only want to consider the probability distribution of a single dimension, we would sum over (or marginalize) all of the other unwanted dimensions. This is not what we are doing in this instance. The equation corresponds to a single probability related to a unique path. We added this statement about marginalization to ensure no confusion given the referee's question, however we believe the meaning is still maintained without it. We have removed the first part of this sentence, keeping only the second part.

\item p5, right column, list item 1: ``node'' meaning one of the circles in Fig. 5? 
\begin{itemize}
\item Yes, the nodes does mean the circles. Thank you, this was confusing and we've made the language more consistent now and refered to the circles when we first mention nodes.
\end{itemize}

\item p5, right column, list item 3: In the example of Fig. 5, since A=1/3 or 0 for each transition, it looks like the selected path just links the states with the highest Fourier amplitude. Is it always that simple?
\begin{itemize}
\item That is a good point and it is not always so simple. In our Figure 5, we have made an example where the signal is particularly loud and can easily be seen by eye, but it is not always the case. In continuous-wave searches we expect that the signal cannot be seen by eye. It might also be the case that there are loud noise fluctuations in time-frequency bins. In this case they may not be selected by the Viterbi algorithm if the overall value of equation 5 is higher for the signal path than the paths containing the noise. 
\end{itemize}

\item p6, left column, after itemized list: delete `expeced to be' 
\begin{itemize}
\item We believe it is important to keep ``expected to be''. The reason is that continuous waves have not yet been detected and although of course we believe they are worth searching for, a more pessimistic person might argue that the signals may not be there at all! 
\end{itemize}

\item p6, left column: How does the assumption of white noise get inserted into the VA? How does this assumption affect the results?
\begin{itemize}
\item The white noise assumption is implicit in that we do not build any knowledge of coloured noise into the analysis. This statement was added in response to referee 3's observation that the noise in our data is not white and they asked how or if we take account of this. We do not take account of non-white noise in our analysis (which is also consistent with LIGO analyses which assume white noise even though LIGO noise is not white). We also note that the narrow frequency range we consider is less impacted by the increase in noise at low frequency. We have added some details to clarify this in the text. 
\end{itemize}

\item p6 right column: If you elimintate the start-up points from the calculation, does E change significantly?
\begin{itemize}
\item We have also computed the $E_{\rm rms}$ value when the first four time bins are ignored. We find a slight impovement in recovery and have added a sentence about this to the manuscript at the end of this paragraph. 
\end{itemize}

\item p7, Fig. 6: It looks like the frequency bins are 0.3 Hz wide and 3s long. Can you estimate the S/N ratio in this data set to illustrate the power of the VA?
\begin{itemize}
\item We can only estimate S/N for single time blocks of data, however we do not believe that a representative S/N can be estimated for the entire data set. 
\end{itemize}

\item p7, right column, Section V, para 2. ``Just to be clear, what have you changed from the apparatus in earlier sections (if anything), other than the photodiode described below? It reads like you have changed something.''
\begin{itemize}
\item The only thing we have changed is replacing the webcam with the photodiode so that the apparatus can be used to capture higher frequency speech and music. In this section we use the interferometer to capture more complicated signals, so we draw comparisons to laser microphones used in other fields. We have added a sentence to this paragraph to clarify the apparatus changes. 
\end{itemize}

\item p8, left column: This paragraph adds very little new information to the topic of Section V, and interrupts the flow of the paper. I recommend shortening it. 
\begin{itemize}
\item Agreed. This paragraph was added in response to reviewer 3's request for us to mention other methods of noise reduction from the gravitational-wave literature. This seemed like the most appropriate place for it to go, however we agree that it is not closely related to the work presented here. We have shortened this discussion to a single sentence and moved the literature review to the Further Reading section in the Supplementary Material. 
\end{itemize}

\item p9 Figure 8: ``It's hard to judge the effectiveness of the filtering on speech intelligibility from the graphs. Here's an idea: we could attach a direct link to an audio clip for each row, perhaps a 10 second recitation of a familiar phrase. It would be available to online readers via s simple click. his ould enhance the discuation sigificantly.''
\begin{itemize}
\item This sounds a great idea! We have collated the four sounds files in this directory \textcolor{orange}{add a link here}. Please let us know if you need any further details from us. 
\end{itemize}

### 2021-07-30 paper/ifo-complexAudio.tex
minor edits

We use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. 
%We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

@@

The raw output of the optical microphone (with anti-aliasing) is noisy with a loud bass continuous hum. 
This can be explained by looking at the power spectral density (PSD) of the background noise (i.e., with the speaker switched off), shown in Fig.~\ref{fig:psd_noise}. 
The spectrum is dominated by AC mains noise with power from the fundamental $50\,{\rm Hz}$ Australian mains power grid signal up to and beyond $8$th harmonic. 
The mains signal is also present but far weaker in the background spectrum taken with the photodiode in darkness, suggesting that ambient lighting has a large contribution. 
Besides lighting, other possible contributions to the mains signal include air conditioning and the photodiode circuit itself. 
The appearance of harmonics of the mains noise is likely due to non-linearity in the system (see also Ref.~\cite{feynman}). 
The spectrum in Fig.~\ref{fig:psd_noise} also has a broad feature at around $750\,{\rm Hz}$, the origin of which is yet to be determined.
Environmental noise reduction for gravitational-wave detectors is an active area of research (see the accompanying Supplementary Material for further information and resources on this topic).

@@

Firstly, we consider two signal processing techniques used in combination: the cascaded notch~\cite{10.5555/541204} and the Wiener filter~\cite{10.5555/151045}. 
A notch filter removes signals within a specific frequency range. 
We want to remove the $50\,{\rm Hz}$ mains noise and harmonics, therefore we use a cascaded notch filter where each notch is centered at each of the harmonics. 
The Wiener filter is an advanced statistical technique that makes use of statistical information from the speech data and noise. 
It amplifies parts of the signal with high signal-to-noise (SNR) ratio while suppressing parts with low SNR. 
The results of the combined cascaded notch and Wiener filter are shown in the third row of Fig.~\ref{fig:notchWienerLogMMSEResults}. 
Most of the mains noise is removed, however the recovered voice sounds muffled and is not understandable.

Secondly, we apply a speech enhancement technique. 
Ref.~\cite{SubjectiveComparison} compares $13$ speech enhancement methods, finding the log minimum mean-square error (logMMSE) estimator to be the best, qualitatively, at recovering speech (see also Ref.~\cite{Ephraim1984SpeechEU_logMMSE} for details on the logMMSE estimator). 
We use an existing implementation of the logMMSE from~\cite{logmmse}.  
The logMMSE estimator results are shown in the bottom panels of Fig.~\ref{fig:notchWienerLogMMSEResults}. 
We see significant attenuation of the mains harmonics and general smoothing of the spectrum. 
Most of the background noise is removed, however, the logMMSE does not significantly enhance the speech as the voice sounds muffled and indistinct.

>>>>

We use the Michelson interferometer as an ``optical microphone'', where a laser is used to detect sound instead of the electrical components in a conventional microphone.
The only change to our apparatus is replacing the webcam with a photodiode to allow us to capture higher frequencies neccessary for speech and music (see Section~\ref{sec:photodiode}). 
Optical microphones have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defense industry and operate on a variety of related principles. 
%We use the term ``optical microphone'' to distinguish this technology from those previous technologies.
Our objective is to play a recording of speech or music through the speaker attached to mirror M2 (see Fig.~\ref{fig:ifo_schematic_webcam}), record the resulting interference pattern, and then recover the original signal via a selection of signal processing techniques.

@@

The raw output of the optical microphone (with anti-aliasing) is noisy with a loud bass continuous hum. 
This can be explained by looking at the power spectral density (PSD) of the background noise (i.e., with the speaker switched off), shown in Fig.~\ref{fig:psd_noise}. 
The spectrum is dominated by AC mains noise with power from the fundamental $50\,{\rm Hz}$ Australian mains power grid signal up to and beyond $8$th harmonic. 
The mains signal is also present, but far weaker, in the background spectrum taken with the photodiode in darkness, suggesting that ambient lighting has a large contribution. 
Besides lighting, other possible contributions to the mains signal include air conditioning and the photodiode circuit itself. 
The appearance of harmonics of the mains noise is likely due to non-linearity in the system (see also Ref.~\cite{feynman}). 
The spectrum in Fig.~\ref{fig:psd_noise} also has a broad feature at around $750\,{\rm Hz}$, the origin of which is yet to be determined.
Environmental noise reduction for gravitational-wave detectors is an active area of research (see the accompanying Supplementary Material for further information and resources on this topic).

@@

Firstly, we consider two signal processing techniques used in combination: the cascaded notch~\cite{10.5555/541204} and the Wiener filter~\cite{10.5555/151045}. 
A notch filter removes signals within a specific frequency range. 
We want to remove the $50\,{\rm Hz}$ mains noise and harmonics, therefore we use a cascaded notch filter where each notch is centered at each of the harmonics. 
The Wiener filter is an advanced statistical technique that makes use of statistical information from the speech data and noise. 
It amplifies parts of the signal with high signal-to-noise (SNR) ratio while suppressing parts with low SNR. 
The results of the combined cascaded notch and Wiener filter are shown in the third row in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
Most of the mains noise is removed, however the recovered voice sounds muffled and is not understandable.

Secondly, we apply a speech enhancement technique. 
Ref.~\cite{SubjectiveComparison} compares $13$ speech enhancement methods, finding the log minimum mean-square error (logMMSE) estimator to be the best, qualitatively, at recovering speech (see also Ref.~\cite{Ephraim1984SpeechEU_logMMSE} for details on the logMMSE estimator). 
We use an existing implementation of the logMMSE from~\cite{logmmse}.  
The logMMSE estimator results are shown in the bottom panels in Fig.~\ref{fig:notchWienerLogMMSEResults}. 
We see significant attenuation of the mains harmonics and general smoothing of the spectrum. 
Most of the background noise is removed, however, the logMMSE does not significantly enhance the speech as the voice sounds muffled and indistinct.

### 2021-07-30 paper/ifo-wanderingTone.tex
minor edits

We simulate a slowly wandering signal by modulating the frequency sinusoidally with a modulation amplitude that decays with time. 
We use the same set-up as shown in Fig.~\ref{fig:ifo_schematic_webcam} and the output interference pattern is recorded via webcam as in Section~\ref{sec:single_tone}. 
In this section, we test the Viterbi algorithm’s ability to recover the wandering signal. 
Note that we implicitly approximate the noise at the webcam as white (uniform in frequency) in this implementation of the Viterbi algorithm. 
This approximation ignores the increase in noise at low frequencies (below 1~Hz) shown in Fig.~\ref{fig:webcam_spectrum} but is a reasonable approximation for the higher-frequency (around 5~Hz) wandering frequency signals that we use.

>>>>

We simulate a slowly wandering signal by modulating the frequency sinusoidally with a modulation amplitude that decays with time. 
We use the same set-up as shown in Fig.~\ref{fig:ifo_schematic_webcam} and the output interference pattern is recorded via webcam as in Section~\ref{sec:single_tone}. 
In this section, we test the Viterbi algorithm’s ability to recover the wandering signal. 
Note that we implicitly approximate the noise at the webcam as white (uniform in frequency) in this implementation of the Viterbi algorithm. 
This approximation ignores the increase in noise at low frequencies (below 1~Hz) shown in Fig.~\ref{fig:webcam_spectrum}.
However, White noise is a reasonable approximation for the narrow frequency range (around $3$--$11\,{\rm Hz}$) we use in this analysis.
